Verifying Demonstrations

### 2017-08-29 conclusions.tex
Adds clarifications, improves slides

  \begin{question}
    Can we achieve receipt freeness and protect from Sybil?
  \end{question}
\end{frame}

@@

  \mode<presentation>{%
    \begin{remark}
      \begin{itemize}
        \item Without anonymous submission we don't get proof privacy, thus no 
          receipt freeness either.
        \item Voting normally uses mix-nets.
        \item Submit over Tor~\cite{Tor}?
      \end{itemize}
    \end{remark}
  }
\end{frame}

>>>>

  \begin{question}
    Can we achieve receipt freeness (deniability) and protect from Sybil?
  \end{question}
\end{frame}

@@

  \mode<presentation>{%
    \begin{remark}
      Without anonymous submission we don't get proof privacy, thus no 
      receipt freeness either.
    \end{remark}
  }
\end{frame}

### 2017-08-29 properties.tex
Removes one of Sébastien's suggested slides
Adds clarifications, improves slides

\mode<presentation>{%
  \only<1>{%
    \begin{idea}[Temporal eligibility]
      \begin{itemize}
        \item We need a partially ordered set (poset).
        \item There is a mechanism that provides this property: a blockchain.
        \item There are also other structures, e.g.\ a directed 
          graph~\cite{BlockchainFreeCryptocurrencies}.
      \end{itemize}
    \end{idea}
  }
  \only<2>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included (duh!).
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<3>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          \ac{tposet}, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

@@

If the proofs are stored publicly, then an individual can check that their 
proof has been included there.
Thus \cref{IndividualVerif} is fulfilled.
Similarly for universal verifiability.
If the storage is public, then anyone can download all the proofs, verify their 
eligibility and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
To have any verifiability, we need the storage to be immutable --- i.e.\ it 
prevents malicious changes.

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}

@@

  \begin{idea}[Universal verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Anyone can download all proofs, verify eligibility and then count 
        them.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Coercion resistance is difficult to achieve for voting.
      \item It doesn't make much sense for protests.
      \item E.g.\ Eve physically brings Alice to a protest she doesn't want to 
        participate in.
      \item That leaves us with receipt freeness and vote privacy.
    \end{itemize}
  \end{remark}
\end{frame}
}

@@

  \begin{question}
    Can we link a verified key to a unique ring signature key?
  \end{question}
\end{frame}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use 
        it to verify that she participated.

@@

      \item But Alice should still not be able to participate twice.
    \end{itemize}
  \end{idea}
\end{frame}
}

\begin{frame}
  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}

@@

  \mode<presentation>{%
    \begin{remark}
      \begin{itemize}
        \item Alice submits her proof.
        \item She stores the hash of the head of the \ac{tposet}.
        \item She removes the proof and signature key.
      \end{itemize}
    \end{remark}
  }
\end{frame}

@@

Similarly, we have the problem of how protesters submit their proofs to the 
system.
This must be done anonymously.
Otherwise Eve can analyse the network traffic to find out who submitted proofs 
to the system.

\begin{frame}
  \begin{question}
    How do we submit the proofs to storage?
    Voting normally uses mix-nets.
    Submit over Tor~\cite{Tor}?
  \end{question}

  \begin{remark}
    Without anonymous submission we don't get proof privacy, thus no receipt 
    freeness either.
  \end{remark}
\end{frame}

>>>>

\mode<presentation>{%
  \only<1>{%
    \begin{idea}[Temporal eligibility]
      \begin{itemize}
        \item We need a partially ordered set (poset).

        \item There is a mechanism that provides this property: a blockchain.
        \item There are also other structures, e.g.\ a directed 
          graph~\cite{BlockchainFreeCryptocurrencies}.
      \end{itemize}
    \end{idea}
  }
  \only<3>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included (duh!).
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<4>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          \ac{tposet}, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

@@

If the proofs are stored publicly, then an individual can check that their 
proof has been included (committed) there.
Thus \cref{IndividualVerif} is fulfilled.
Similarly for universal verifiability.
If the storage is public, then anyone can download all the proofs, verify their 
eligibility and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
To have any verifiability, we need the storage to be immutable --- i.e.\ it 
prevents malicious changes.

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Individual verifiability]
    \begin{itemize}
      \item Proofs are stored (committed) publicly.
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}

@@

  \begin{idea}[Universal verifiability]
    \begin{itemize}
      \item Proofs are stored (committed) publicly.
      \item Anyone can download all proofs, verify eligibility and then count 
        them.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<none>{%
\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Coercion resistance is difficult to achieve for voting.
      \item It doesn't make much sense for protests.
      \item E.g.\ Eve physically brings Alice to a protest she doesn't want to 
        participate in.
      \item That leaves us with receipt freeness and vote privacy.
    \end{itemize}
  \end{remark}
\end{frame}
}

@@

  \begin{question}
    Can we link a verified key to a unique ring signature key?
  \end{question}

  \begin{question}
    How to submit the proofs to the system?
  \end{question}
\end{frame}

@@

\mode<presentation>{%
\begin{frame}
  \begin{remark}
    The proof itself is a sort of receipt.
  \end{remark}

  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the \ac{tposet}.
      \item She removes the proof and signature key.
    \end{itemize}
  \end{idea}
\end{frame}
}

\begin{frame}
\mode<presentation>{%
  \begin{idea}
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use it 
        to verify that she participated.

@@

      \item But Alice should still not be able to participate twice.
    \end{itemize}
  \end{idea}
}

@@

  \begin{question}
    Is there such a signature scheme?
    Can we construct it?
  \end{question}
\end{frame}

@@

Similarly, we have the problem of how protesters submit their proofs to the 
system.
This must be done anonymously.
Otherwise Eve can analyse the network traffic to find out who submitted proofs 
to the system.
The main problem here is that the participants must be indistinguishable from 
non-participants.
This means that we cannot use special-purpose anonymizing 
technologies.

\begin{question}
  How do we submit the proofs to storage?
  Voting normally uses mix-nets (provable shuffles).
\end{question}

\begin{remark}
  We must mix participants with non-participants.
\end{remark}
